\documentclass{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{array}
\usepackage{geometry}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{cite}
\usepackage{xr}
\usepackage{xr-hyper}

\externaldocument[SRS-]{../SRS/SRS}

\hypersetup{ colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with
                             %linkbordercolor)
    citecolor=green,        % color of links to bibliography
    filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}


\title{Hazard Analysis\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}


\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist

\newcommand{\cellrule}{\par\vspace{-0.3em}\noindent\rule{\linewidth}{0.2pt}\par}

\setlength{\parindent}{0pt}

\begin{document}

\maketitle
\thispagestyle{empty}

~\newpage

\pagenumbering{roman}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
2025-10-06 &  Nirmal, Sathurshan, Omar, Kalp, Jay & Initial Write-up\\
2025-10-26 & Sathurshan & Update sampling rate requirement\\
2025-11-06 & Sathurshan & Provided rationale for roadmap\\
2025-11-06 & Sathurshan & Traceability of safety requirements to SRS\\
2025-12-12 & Omar & Add linking between FMEA table and safety requirements.\\
\bottomrule
\end{tabularx}
\end{table}

~\newpage

\tableofcontents

~\newpage

\pagenumbering{arabic}

\section{Introduction}

A hazard is anything that prevents the Audio360 system from notifying users with
important sounds near them with high precision and accuracy. For deaf and
hard-of-hearing individuals who rely on the system for situational awareness,
any failure to detect, classify, or display audio information could result in
missed safety cues, social interactions, or degraded environmental awareness.

This hazard analysis identifies potential failure modes in the Audio360 audio
localization system and establishes safety requirements to ensure reliable
operation in real-world scenarios.

\section{Scope and Purpose of Hazard Analysis}

The scope of this document is to identify possible hazards within the Audio360
system components, the effects and causes of failures, mitigation steps, and
resulting safety and security requirements.

Potential losses that could be incurred due to system failures include physical
injury from missed emergency vehicle warnings or approaching machinery,
household accidents from undetected safety alerts, missed social interactions
and communication opportunities, reduced independence and confidence in daily
activities, and loss of user trust in the assistive technology system.

\section{System Boundaries and Components}

This section is broken down into two subsections: one for components within the
system boundary, and one for components outside the system boundary.

\subsection{Inside the System Boundary}

The following components are within the system's control and responsibility:

\begin{itemize}
\item \textbf{Embedded firmware:} Real-time operating system and all embedded
software running on the processing unit.

\item \textbf{Signal processing module:} Real-time digital signal processing
algorithms including frequency domain transforms, filtering, and time-domain
analysis.

\item \textbf{Direction of arrival (DoA) estimation:} Algorithms for computing
sound source direction on a 2D plane based on time difference of arrival and
phase differences across microphones.

\item \textbf{Audio classification engine:} Sound fingerprinting and
classification logic to identify and categorize detected sounds (e.g., speech,
vehicles, alarms).

\item \textbf{Visualization Controller:} \label{comp:viz_controller} Component
responsible for creating and sending visualization output to the glasses.

\item \textbf{Configuration and calibration:} Microphone array calibration
routines and system configuration parameters.
\end{itemize}

\subsection{Outside the System Boundary}

The following external entities interact with the system but are not under its
direct control:

\begin{itemize}
\item \textbf{Users:} Individuals who are deaf or hard of hearing wearing the
device. Their actions, responses to alerts, and interpretation of displayed
information are outside the system's control.

\item \textbf{Environmental sounds:} Acoustic signals in the physical
environment, including speech, vehicle noises, alarms, and ambient sounds. The
system detects and processes these but does not generate or control them.

\item \textbf{Audio capture subsystem:} Synchronized sampling logic for the
microphone array, including analog-to-digital conversion interfaces and buffer
management. This component is included in the microcontroller and is not within
our system's control.

\item \textbf{Physical microphone hardware:} Microphone sensors that capture
acoustic pressure waves. While the system controls their digital interface, the
physical transduction mechanism is external.

\item \textbf{Smart glasses hardware:} The physical display device, including
its screen, optics, power management, and form factor. The system sends display
commands but does not control the hardware's internal operation.

\item \textbf{Microcontroller:} \label{comp:microcontroller} Component
responsible for processing real time data of sensor inputs. This hardware
component's performance and reliability are outside our system's control.

\item \textbf{Power supply:} Battery or external power source providing
electrical power to system components. Power management at the hardware level is
external to the software system.

\item \textbf{Physical environment:} Room acoustics, ambient noise levels,
temperature, and other environmental factors that affect sound propagation and
microphone performance.
\end{itemize}



\section{Critical Assumptions}

\begin{enumerate}
    \item Microphone
    \begin{itemize}
        \item All microphones are able to capture frequencies between at least
        250 Hz to 8 kHz, which covers most of the frequency range of human
        hearing.
        \cite{MiracleEar2025}.
        \item Microphones operate correctly within normal operating temperatures
        of 0-35°C. 
    \end{itemize}
    
    \item Microcontroller
    \begin{itemize}
        \item The analog-to-digital converters (ADC) that comes with the
        hardware provides stable conversions in real-time.
        \item Processor's clock frequency remains stable under normal operating
        temperatures 0-35°C.
    \end{itemize}

    \item Output Display
    \begin{itemize}
        \item Visual indicators on the smart glasses remain visible in
        all lighting conditions. This includes outdoor with sun and indoor with
        no light. 
    \end{itemize}

    \item System Integration
    \begin{itemize}
        \item Voltage and power is maintained by the controller firmware itself
        and we do not need to manage that in software. 
    \end{itemize}
    
\end{enumerate}

\section{Failure Mode and Effect Analysis}

\subsection{Severity Mapping Table}
The severity, occurrence, and detection ratings used in the FMEA table are
defined as follows:
\begin{table}[H]
\begin{tabular}{c|c|c|c}

    Rating & Severity & Occurrence & Detection \\\hline
    1 & Negligible & Rare & Always detected \\\hline
    2 & Minor & Uncommon & Easy to detect \\ \hline
    3 & Major & Occasional & Moderately difficult to detect \\\hline
    4 & Critical & Frequent & Difficult to detect \\\hline
    5 & Catastrophic & Very frequent & Impossible to detect \\


\end{tabular}
\end{table}

\subsection{Priority Mapping Table}

The priority level is determined by the summation of the severity, occurrence,
and detection ratings:

\begin{table}[H]
    \begin{tabular}{c|c}
        Product of severities & Priority Level \\\hline
        1 - 4 & Low Priority \\\hline
        5 - 10 & Medium Priority \\\hline
        10 - 15 & High Priority \\

    \end{tabular}
\end{table}

\newpage
\pdfpagewidth=15in \pdfpageheight=11.5in
\newgeometry{left=1.5cm, right=1cm, top=1cm, bottom=1cm}

    
    \begin{longtable}{ >{\raggedright\arraybackslash}p{0.5cm}%     (\#)
        >{\raggedright\arraybackslash}p{3.0cm}%   (Component)
        >{\raggedright\arraybackslash}p{3.0cm}%   (Potential Failure)
        >{\raggedright\arraybackslash}p{3.0cm}%   (Effect on User)
        >{\raggedright\arraybackslash}p{3.0cm}%   (Likely Cause)
        >{\centering\arraybackslash}p{1.5cm}%   (Severity)
        >{\centering\arraybackslash}p{2.4cm}%     (Occurence Frequency)
        >{\raggedright\arraybackslash}p{3.0cm}%     (Detection Method)
        >{\centering\arraybackslash}p{2.0cm}%     (Detection Likelihood)
        >{\centering\arraybackslash}p{2.4cm}%   (Priority)
        >{\raggedright\arraybackslash}p{3.0cm}%     (Recommended Mitigation)
        >{\raggedright\arraybackslash}p{3.0cm}%
      }

    \toprule
    \textbf{\#} & \textbf{Component / Function} & \textbf{Potential Failure
    Mode} & \textbf{Effect on User / System}& \textbf{Likely Cause(s)} &
    \textbf{Severity} & \textbf{Occurrence Frequency} & \textbf{Detection
    Method} & \textbf{Detection Likelihood} & \textbf{Priority \hspace{15pt}(S +
    O + D)} & \textbf{Recommended Action} & \textbf{Relevant Requirement(s)}\\
    \midrule
    \endfirsthead
    \toprule
    
    \midrule
    \endhead

    \label{fmea:microphone}
    1 & Microphone &  Unresponsive / Distorted Microphone. & Not able to
    effectively localize audio. \cellrule Unable to provide warnings to user. &
    Microphone circuit failure. \cellrule Microphone damage. \cellrule Excessive
    ambient noise. & 5 & 1  & Multiple corrupted microphone data frames.
    \cellrule Excessive white noise detection. \cellrule Short circuit detection
    for microphones. & 3 & 9 & Detect failure using microphone audio (or lack
    thereof) and notify user. & FR1.4, FR2.3, FR3.5, FR7.2, NFR2.1  \\

    \midrule
    \label{fmea:visualization_controller}
    2 & Visualization Controller & Disconnection from display. & Unable to
    provide visual notifications to user. & Depending on connection type: cable,
    wireless interference, dropped connection. & 3 & 2 & Loss of connection
    signal. \cellrule Failure to send data to display. & 1 & 6 & There are no
    safety requirements that can mitigate this hazard. & NFR2.1\\

    \midrule

    \label{fmea:embedded_firmware}
    3 & Embedded Firmware & System crashes and freezes. & The system remains
    unusable until it is restarted. \cellrule Unable to provide notifications to
    user. & Software bugs. \cellrule Insufficient Error Handling \cellrule
    Insufficient Requirements. & 5 & 3 & System watchdog timer \cellrule Halt
    Interrupt. & 1 & 9 & Implement a watchdog timer to reset the system in the
    event of a crash. \cellrule Implement adequate logging to diagnose the cause
    of firmware failure during post-mortem. \cellrule Robust testing and error
    handling. & FR1.3, FR4.1, FR4.4 \\
    \midrule
    \label{fmea:sound_detection}
    4 & Sound Detection (Audio360 Engine)& Failure to detect important sounds. &
    Failure to notify user of critical sounds. & Insufficient microphone
    quality. \cellrule Poor classification algorithm. \cellrule Excessive
    ambient noise. & 4 & 3 & This is difficult to detect without extensive
    testing. \cellrule Impossible to detect in production. & 5 & 12 & Have a
    thorough library of sounds to detect and test against. \cellrule Measure
    microphone performance on sound library. & FR3.5, FR4.4, FR5.1, FR6.1  \\

    \midrule
    \label{fmea:sound_classifier}
    5 & Sound Classifier (Audio360 Engine) & Misclassification of sounds. &
    Notify the user of the wrong sounds. & Insufficient classification algorithm
    \cellrule Insufficient microphone quality. & 3 & 2 & This is difficult to
    detect without extensive user testing.\cellrule Impossible to detect in
    production. & 5 & 10 & Extensive testing in real-world environments and
    simulation. \cellrule Verify microphone quality during operation. & FR4.4,
    FR5.1, FR5.4, NFR5.1, NFR5.2 \\


    \midrule
    \label{fmea:sound_localizer}
    6 & Sound Localizer (Audio360 Engine) & Inaccurate direction determination
    for sounds. & Misinform the user of the direction of important sounds. &
    Incorrect localization algorithm. \cellrule Insufficient microphone quality.
    & 4 & 2 & This is difficult to detect without extensive localization
    testing. \cellrule Impossible to detect in production. & 5 & 11 & Extensive
    localization testing in real-world environments and simulation. & FR5.2,
    NFR5.3 \\
    
    \bottomrule
    \end{longtable}

\restoregeometry

\pdfpagewidth=8.5in \pdfpageheight=11in

\subsection{Out of Scope Failure Modes}
The project involves off the shelf hardware components with their own possible
failure modes and possible mitigations. Since the hardware (micro-controller, 
microphones, glasses) and electrical components are not being designed as 
part of the project, these failure modes are considered out of scope:
\begin{itemize}
    \item Battery failure / damage.
    \item Physical display damage.
    \item Power supply issues.
    \item Physical damage to the glasses.
    \item Comfort issues resulting from usage of the glasses.
\end{itemize}


\section{Safety and Security Requirements}

\begin{itemize}
    \item \label{SR1}\textbf{SR1:} The micro-controller shall run the main
    \progname ~software in a closed environment. No external devices other than
    the microphones and output display shall be able to connect to it. This
    ensures protection against unauthorized access.

    \item \label{SR2}\textbf{SR2:} The system shall permanently discard
    microphone audio data immediately after completion of audio analysis. This
    requirement ensures data privacy and prevents unauthorized reuse of raw
    audio.

    \item \label{SR3}\textbf{SR3:} The system shall detect and flag audio
    anomalies such as clipping, lost signal and silence. This enables
    identification of microphone or signal path faults.

    \item \label{SR4}\textbf{SR4:} The system shall disable audio classification
    and directional analysis features until microphone faults addressed in
    \hyperref[SR3]{SR3} are resolved. This prevents the generation of unreliable
    or unsafe outputs.

    \item \label{SR5}\textbf{SR5:} The visualization controller shall present
    information in a non-intrusive manner, minimizing visual
    obstruction so users can safely perform external activities. This allows the
    user to wear the glasses and perform daily activities without distraction.

    \item \label{SR6}\textbf{SR6:} The visualization controller component shall
    alert users when the core safety features such as direction
    determination or classification fail. This ensures that users are aware of
    degraded safety functions.

    \item \label{SR7}\textbf{SR7:} The system shall have an audio processing
    success rate end to end of 100\%. All user core features depends on this
    component, thus, it must work every time. This mitigates classification
    related hazards identified in the FMEA.

    \item \label{SR8}\textbf{SR8:} The system shall
    notify users when a sound classification result has low confidence
    (predicted accuracy of classification prediction $<$ treshold) or is
    unrecognized to prevent misleading contextual feedback.

    \item \label{SR9}\textbf{SR9:} The system shall estimate the
    direction of arrival of an audio source with a maximum error of
    \hyperref[SRS-symbol:theta_e]{$\theta_e$} radians.
    This ensures reliable directional awareness for the user.

    \item \label{SR10}\textbf{SR10:} The system shall perform continuous
    diagnostics on all hardware components to monitor hardware errors in
    real-time. This ensures the system can react to failures as soon as they
    occur.
    
\end{itemize}

\begin{table}[h!]
\centering

\begin{tabular}{lll}
\toprule
\textbf{Safety Requirement} & \textbf{Requirement from SRS} & \textbf{Failure Mode}\\
\midrule
\hyperref[SR1]{SR1} & \hyperref[SRS-FR9_1]{FR9.1} & \textbf{N/A}\\
\hyperref[SR2]{SR2} & \hyperref[SRS-NFR4_3]{FR4.3} & \textbf{N/A}\\
\hyperref[SR3]{SR3} & \hyperref[SRS-FR3_5]{FR3.5} & \hyperref[fmea:microphone]{Microphone failures}\\
\hyperref[SR4]{SR4} & \hyperref[SRS-FR4_4]{FR4.4} & \hyperref[fmea:microphone]{Microphone failures}\\
\hyperref[SR5]{SR5} & \hyperref[SRS-NFR6_2]{NFR6.2} & \hyperref[fmea:visualization_controller]{Visualization controller failures}\\
\hyperref[SR6]{SR6} & \hyperref[SRS-FR6_2]{FR6.2} & \hyperref[fmea:microphone]{Microphone failures} and \hyperref[fmea:embedded_firmware]{embedded firmware}\\
\hyperref[SR7]{SR7} & \hyperref[SRS-NFR3_3]{FR3.3} & \hyperref[fmea:sound_classifier]{Audio360 Engine} \\
\hyperref[SR8]{SR8} & \hyperref[SRS-FR5_4]{FR5.4} & \hyperref[fmea:sound_classifier]{Sound classifier}\\
\hyperref[SR9]{SR9} & \hyperref[SRS-NFR5_3]{NFR5.3} & \hyperref[fmea:sound_localizer]{Sound localizer}\\
\hyperref[SR10]{SR10} & \hyperref[SRS-FR1_4]{FR1.4} & \hyperref[fmea:embedded_firmware]{Embedded firmware}\\
\bottomrule
\end{tabular}
\caption{Safety requirements traceability to SRS requirements and FMEA table.}
\end{table}

\section{Roadmap}

The following safety and security requirements are planned for implementation
within the scope of the capstone project timeline. All these requirements are
necessary and feasible in a 6 month development period.
\begin{itemize}
    \item \hyperref[SR2]{SR2}
    \item \hyperref[SR3]{SR3}
    \item \hyperref[SR4]{SR4}
    \item \hyperref[SR5]{SR5}
    \item \hyperref[SR7]{SR7}
    \item \hyperref[SR8]{SR8}
    \item \hyperref[SR9]{SR9}
\end{itemize}

The following safety and security requirements are identified as stretch goals.
Their implementation will depend on the available development bandwidth and
project progress:
\begin{itemize}
    \item \hyperref[SR6]{SR6}: This requirement is a stretch goal as
    visualization output on glasses is limited. Core features of the glasses
    are being prioritized as safety features.
    \item \hyperref[SR10]{SR10}: This requirement will be implement to some
    extent. Diagnostics for the microphones will be implemented as all core
    features of \progname~depends on the microphones. Other diagnostics, such
    as ones for output display, are less priority.
\end{itemize}

\newpage
\bibliographystyle{IEEEtran}
\bibliography{../../refs/References}

\newpage{}

\section*{Appendix --- Reflection}

\begin{enumerate}
    \item What went well while writing this deliverable? 
    
    \textbf{Sathurshan:} The team had a strong understanding of the
    safety-critical nature of the system. Some members of the team also had
    experience in writing a Hazard Analysis document from extra-curricular
    activities. This made performing the hazard analysis more straightforward,
    as we were able to effectively identify and evaluate potential risks within
    the system.

    \textbf{Kalp:} I think having written the SRS document before this one made
    the hazard analysis more straightforward, as we had a clear understanding of
    the system and the risks associated with it. We had many discussions during
    the SRS document that really clarified the requirements and the expected
    software states of the system, really helping us quickly go through this
    document without much difficulty.
    
    \textbf{Nirmal Chaudhari:} For this deliverable, I focused on the critical
    assumptions section. What worked well while writing this deliverable was
    having a clear enough picture of constraints that exist with this project
    from the environment section of the SRS doc. From these constraints, it
    became clear what is out of our hands, and needs assumptions for our project
    to validate the requirements we have set. 

    
    \textbf{Omar:} I think what went well when writing this document was the
    cross collaboration between myself and Sathurshan. We were able to have in
    depth discussions about the potential hazards and risks from different
    components since he was responsible for most of the technical requirements.
    This was instrumental in ensuring a detailed and accurate FMEA table.

    \textbf{Jay:} The FMEA structure provided a clear framework for thinking
    through potential failures systematically. Breaking down each component and
    considering what could go wrong helped us identify risks we might have
    otherwise missed. The team's collaborative approach also meant we could
    challenge each other's assumptions and ensure we weren't overlooking
    critical failure modes.

    \item What pain points did you experience during this deliverable, and how
    did you resolve them?

    \textbf{Sathurshan:} Some sections of this deliverable were dependent on the
    completion of other sections within this document and the SRS. As a result,
    managing the timeline for these sections was challenging. To resolve this,
    we coordinated closely with the owners of the dependent sections, which
    improved collaboration and allowed us to exchange constructive feedback to
    ensure consistency across the document.

    \textbf{Kalp:} I think the main pain point was that there was high
    dependence between the sections of the document. This lead to us assigning
    the tasks to each person in large chunks (to avoid the issues we ran into
    during the SRS document), but then that left us with people not having much
    to contribute to on the document. We ended up having to reshuffle the tasks
    around to help mitigate this issue. 
    
    \textbf{Nirmal Chaudhari:} While working on this deliverable, it sometimes
    became unclear what should be listed as an assumption vs constraint. As we
    continued brainstorming however, we started to look at it from another angle
    where the assumptions are technically just listed as boundaries that our
    system has, and requires assumptions. Moreover, referencing between the
    sections other people are working on for consistency was a difficult task to
    do, especially within a small time frame.  

    \textbf{Omar:} One pain point I experienced was ensuring that the FMEA table
    was well formatted and readable. Adjusting the latex code to ensure that the
    table fit within the page margins while still being legible was a challenge.
    I resolved this by experimenting with different table types and packages,
    even adjusting page sizes till it worked. 

    \textbf{Jay:} Initially, it was difficult to assess the severity and
    likelihood of different failure modes objectively. We had to balance being
    thorough without being overly pessimistic about every possible edge case. I
    resolved this by focusing on realistic operating conditions and consulting
    with teammates who have more hardware experience to ground my estimates in
    practical constraints.

    \item Which of your listed risks had your team thought of before this
    deliverable, and which did you think of while doing this deliverable? For
    the latter ones (ones you thought of while doing the Hazard Analysis), how
    did they come about?

    \textbf{Sathurshan:} Before this deliverable, I had already identified the
    risk of microphone failures, as it serves as the system's primary input.
    During the hazard analysis, we also identified the risk of unauthorized
    access to system components, particularly data stored on the microcontroller
    and modification of the software. This risk emerged as we considered
    non-physical hazards, which the following questions allude to.

    \textbf{Kalp:} A big risk that I think the team was was already considering
    before the deliverable was risk of hardware failure (microphone, smart
    glasses, microcontroller, etc.). This was mainly due to us just thinking
    mainly about the high level system, with the hardware being major components
    of that mental model. During the document is when I would say we started to
    think more about security and privacy risks, specifically with data access
    breach and unauthorized access to the system.
    
    \textbf{Nirmal Chaudhari:} One of the listed risks we thought of before the
    deliverable was not being able to find a microcontroller with 4 ADCs with
    the limited budget we had. This risk was highlighted to us by our supervisor
    from our initial meeting. One risk we though about while doing this
    deliverable was risks associated with the environment, which we have no
    control over. During our team brainstorming section, we realized that
    weather conditions like rain, humidity, wind are things our system will have
    to be robust enough to handle given the limited budget we have. To address
    these risks, we added in our critical assumption that for the scope of this
    project we will have perfect weather conditions. 

    \textbf{Omar:} Prior to this deliverable, I had already considered the risk
    of system crashes and freezes due to my experience with embedded systems.
    During the hazard analysis, we had to delve further into the specific
    connection mechanism that the smart glasses provide. This led to the
    identification of the risk of disconnection from the display, which I had
    not previously considered.

    \textbf{Jay:} We had already considered the risk of classification errors
    and inaccurate direction estimation since those are core to the system's
    value proposition. What emerged during the hazard analysis was thinking
    about failures, where one component's malfunction could propagate through
    the system and cause misleading outputs rather than obvious failures. This
    came from systematically working through the FMEA table and considering how
    each failure mode affects downstream components.

    \item Other than the risk of physical harm (some projects may not have any
    appreciable risks of this form), list at least 2 other types of risk in
    software products. Why are they important to consider?

    \textbf{Sathurshan:} Other forms of software-related risks include data
    privacy violations and security vulnerabilities that allow unauthorized
    access without user consent. These are critical to consider because they can
    user data can be used against them, resulting in ethical consequences.

    \textbf{Kalp:} I think two forms of software-related risks that are
    important to consider are data privacy violations and reliability issues.
    With many software systems dealing with data from the user, or providing
    important data to the user, it's important to consider the risks of data
    being leaked / breached (make private information public or inform the user
    something wrong potentially misguiding their actions).

    \textbf{Nirmal Chaudhari:} One other type of risk that exists with software
    projects is security and privacy risks. While working on the environment
    section of the SRS document, I realized there are a lot of legal constraints
    around collecting and analyzing sounds in a given environment. This is
    important to consider, since if its left unaddressed moving the system into
    a production environment would be impossible. Another type of risk that
    exists is environmental risks. If the battery we choose is inefficient or is
    harmful to the environment when being disposed of, this would negatively
    impact the environment around us. 

    \textbf{Omar:} Two other types of software-related risks include performance
    degradation over time. This is an important issues with emerging
    technologies that rely on machine learning models, as they may become less
    effective as the environment and sensors change overtime, even on the same
    hardware. Another risk is bad UI/UX design, which can lead to user
    frustration and abandonment of the product. This is especially important to
    consider for assistive technologies, as they need to be intuitive and easy
    to use for individuals with varying levels of ability.

    \textbf{Jay:} Two important risks are loss of user confidence and poor code
    maintainability. If the system gives false alarms or inconsistent results,
    users will stop trusting it and won't rely on it when they actually need it.
    Maintainability is also critical because if the code is messy or poorly
    organized, fixing bugs later becomes risky and time-consuming, which is
    especially problematic for a safety device that needs to stay reliable over
    time.
\end{enumerate}

\end{document}