\documentclass{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}

\title{Development Plan\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
2025-09-22 & Nirmal, Sathurshan, Omar, Kalp, Jay & Initial Write-up\\
\bottomrule
\end{tabularx}
\end{table}

\newpage{}

This document describes the development plan for the spatial awareness device
\textit{audio360}. It contains internal logistics that our team will adhere to,
and measures in place to ensure the confidentiality of our device.

\section{Confidential Information?}

There is no confidential information to protect.

\section{IP to Protect}

There is no IP to protect.

\section{Copyright License}

Our team will be adopting the MIT
\href{https://github.com/Nirmal-code/SixSense/blob/main/LICENSE}{License}.

\section{Team Meeting Plan}

The team will meet twice a week in-person at a predetermined location. Each
meetings will limited to a maximum of 30 minutes. Additional meetings may be
scheduled as needed during lecture times if course instructor has no content to
share. Team meetings will be organized by the the
\hyperref[role:meeting_chair]{meeting chair} and follow the agenda similar to
below:

\begin{itemize}
  \item Individual blockers/updates since last time met (10 minutes)
  \item Individual next steps discussions (3 minutes)
  \item Pre-determined questions (7 minutes)
  \item Additional discussions (10 minutes)
\end{itemize}

The team will meet with the project advisor in-person once every two weeks, on
Mondays from 12:30 pm to 1:00 pm. If the team finds that an in-person meeting
with the advisor is not necessary, the team will send a concise update through
email.

Meetings with advisor will be organized by the
\hyperref[role:meeting_chair]{meeting chair} and follow an agenda similar to
below:

\begin{itemize}
  \item Team updates from the past 2 weeks (5 minutes)
  \item Pre-determined questions (15 minutes)
  \item Additional discussions (10 minutes)
\end{itemize}

\section{Team Communication Plan}

The team will use the following communication methods for each of the scenarios
listed:
\begin{itemize}
  \item \textbf{General team communication:} Microsoft Teams Group Chat. Every
  team member is expected to send general queries and updates to the group chat.
  Try to avoid sending individual messages to team members regarding the project
  unless necessary.
  \item \textbf{Urgent team communication:} Microsoft Teams Group Chat and
  individual text messages. If a message is urgent, it should be marked as
  urgent in the group chat. If no response is received, individual text messages
  (SMS) can be sent to team members.
  \item \textbf{Communication with the instructor, TA, and supervisor:}
  University email with Outlook. Every team member is expected to be cc'd on
  emails sent to the instructor, TA, or supervisor.
  \item \textbf{Sharing Documents:} Github repository and Microsoft OneDrive.
  All project-critical documents need to be stored in the Github Repository.
  Large files that are not project-critical (e.g datasets, SDKs, etc.) can be
  stored in the university hosted OneDrive.
  \item \textbf{Development communication:} Github Issues and Merge Requests.
  All development-related communication that needs to be tracked for
  traceability should be done through Github Issues and Merge Requests. This
  ensures that critical communication and decisions are documented and can be
  referenced later if needed.
  \item \textbf{Meeting Scheduling:} If a meeting needs to be scheduled outside
  of regular team meetings and involves multiple team members, we will be using
  the Outlook Calendar to find a suitable time for everyone. It is expected that
  all team members will export their calendars to Outlook to reflect accurate
  availability. For one-on-one meetings, direct communication through MS Teams
  is encouraged. If a meeting needs to be scheduled with the instructor, TA, or
  supervisor, the team will use email to coordinate a suitable time. 
\end{itemize}

\section{Team Member Roles}

\begin{itemize}
  \item Leader (Sathurshan Arulmohan)
    \begin{itemize}
      \item Point of contact for professor and TAs. 
      \item Ensures that the team is on track to meet deadlines.
      \item Project planning and scheduling.
    \end{itemize}
  \item Meeting chair (Kalp Shah) \label{role:meeting_chair}
    \begin{itemize}
      \item Creates the agenda for meetings.
      \item Facilitates the meetings.
      \item Ensures that the team sticks to the agenda.
    \end{itemize}
  \item Reviewer (Jay Sharma)
    \begin{itemize}
      \item Reviews all deliverables before deadline to ensure all sections are
      completed.
      \item Reach out to the reviewers of each section to ensure they approve it
      before the deadline.
    \end{itemize}
  \item Note taker (Nirmal Chaudhari)
    \begin{itemize}
      \item Takes notes during meetings.
      \item Create meeting notes summary after the meeting ends to grasp meeting
      content.
      \item Coordinates with project leader after meeting ends for action items. 
    \end{itemize}
  \item System Specialist (Omar Alam)
    \begin{itemize}
      \item Manages and validates system design at a high level. 
      \item Responsible for hardware \& software interfaces.
      \item Handles budgeting and expenses, ensures total budget remains under
      \$500.
    \end{itemize}
\end{itemize}

\section{Workflow Plan}

Git will be used for version control and collaboration. Each branch will
correspond to one or more issue in our Kanban board, with the following naming
convention \texttt{issue/\#<issue-number1>-\#<issue-number2>-...}. If an issue
has multiple sub-issues, then the sub-issues shouldn't be included in the branch
name, only the parent issue number(s). Moreover, each commit should include what
is being worked on (doc, fix, feature, test), the issue number that is being
worked on, and a one line description of what was done. For traceability, each
commit made to the branch should be specific to one issue.\\\\

When an issue is ready for review, a pull request must be created and assigned
to at least one member of our team. For traceability reasons, all issues
addressed in a PR must be linked in the \texttt{development} section. Github
automatically makes this mapping if the issue number is in the commit message,
which is why it's a rule. The repository settings have been configured so that
each PR requires at least 1 approval before being merged. A default
\href{https://github.com/Team6-SixSense/audio360/blob/main/.github/pull_request_template.md}{template}
for PRs has also been created so the assignee can provide information of what
exactly is done in that PR, and for all PRs to follow a consistent format. A PR
should never be force merged into main if it contains pipeline errors.\\\\

Issues will be managed using the Kanban board projects linked to our github
repository. We will have one general Kanban board project for miscellaneous
tasks like adding more github workflows, and then one Kanban board project for
every major deliverable. Each Kanban board project will have the same structure,
with columns for Backlog, To Do, In Progress, In Review, and Done. Each issue
will be assigned to a team member before it is moved to the "In Progress"
column. Issues should only be moved to "In Review" when the work is complete and
a PR has been created. Once the PR has been approved and merged, the issue can
be moved to "Done". We will be using labels to classify the type of issue that
was created. The following labels will be used: documentation, bug, Development,
enhancement, meeting and Research.

\begin{table}[h!]
\centering
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Label} & \textbf{Description} \\ \hline
Documentation & Tasks related to updating any of the files in the \texttt{/doc}
folder of this repository, or any readme files for the project. \\ \hline
Bug & Issues or errors in the system that need to be fixed. \\ \hline
Development & Active system implementation work for new features and/or core
functionality. \\ \hline
Enhancement & Improvements to existing features. Note: Development refers to new
features that are introduced. This label is used if improvements are made to
existing features. \\ \hline
Meeting & Scheduled discussions, planning sessions, or syncs between team
members. \\ \hline
Research & Exploration, investigation, or prototyping to guide future
development \\ \hline
\end{tabularx}
\caption{CLassification Labels}
\end{table}



\section{Project Decomposition and Scheduling}

We will be using Github Projects, more specifically Kanban boards, to decompose
and schedule our main
\href{https://github.com/Team6-SixSense/audio360/milestones}{milestones}. Our
Kanban boards will be available in the
\href{https://github.com/orgs/Team6-SixSense/projects}{projects} tab of our
github organization. \\

We will have one general Kanban board for the entire project, for miscellaneous
tasks that don't directly related to any main milestone. In addition, each main
milestone will have its own Kanban board to track progress and decompose the
deliverables into smaller tasks specific to that milestone. Listed below are a
list of the main milestones (with deadlines) for which we will create Kanban
boards for. Note, the dates listed in each milestone are subject to change.

\begin{enumerate}
  \item Problem Statement, POC Plan, Development Plan (2025-09-22)
  \item Req.\ Doc.\ and Hazard Analysis Revision 0 (2025-10-6)
  \item V\&V Plan Revision 0 (2025-10-27)
  \item Design Document Revision -1 (2025-11-10)
  \item Proof of Concept Demonstration (2025-11-11 to 2025-11-28)
  \item Design Document Revision 0 (2026-01-19)
  \item Revision 0 Demonstration (2026-02-02 to 2026-02-13)
  \item V\&V Report and Extras Revision 0 (2026-03-09)
  \item Final Demonstration Revision 1 (2026-03-23 to 2026-03-29)
  \item Final Documentation Revision 1 (2026-04-06)
  \item EXPO Demonstration (TBD)
\end{enumerate}

\section{Proof of Concept Demonstration Plan}

\wss{What is the main risk, or risks, for the success of your project?  What
will you demonstrate during your proof of concept demonstration to convince
yourself that you will be able to overcome this risk?}

\hspace{1cm}

The biggest risk for the success of the project is the risk of not having a
synchronized microphone array that can recognize the directionality of an audio
source. This is the fundamental technology that the rest of the project and
strech goals are build upon (excluding the audio classification pipeline).

The goal of the proof of concept demonstration is to showcase the functionality
of a microphone array on a controlled environment - a table top lab surface. The
microphone array should be synchronized and capable of recognizing the
directionality of a single audio source (sine frequency sound) with a maximum
error of 45 degrees on the 2D plane of the table. Though this demonstration
doesn't showcase the ability of recognizing multiple audio sources with the
directional microphone array on a smart glasses frame (which is the final goal),
it showcases the feasibility of recoginizing the directionality of an audio
source anywhere on a 2D plane with adequete accuracy. If successful, this would
give us confidence to extend the project with the
\hyperlink{audio_classification_pipeline}{audio classification pipeline},
development of recognizing more than one audio source, extending the audio
analysis pipeline onto the smart glasses, and audio filtering on direction. 

\section{Expected Technology}

\subsection{Programming Languages}
The following programming languages will be used throughout the project.
\begin{itemize}
  \item \textbf{C/C++}: For developing embedded software running on the
  microcontroller.
  \item \textbf{Python}: For prototyping features and visualizing collected data
  for analytics.
\end{itemize}

All C/C++ header files and Pyhon code will include docstrings describing every
file, class, and function to aid contributors. Docstring format will follow the
convention outlined in the project's \nameref{sec:coding_standards}.

\subsection{Libraries}

\textbf{C/C++ Libraries}
\begin{table}[h!]
\centering
\begin{tabularx}{\textwidth}{|l|X|X|}
\hline
\textbf{Library} & \textbf{Description} & \textbf{Usage} \\ \hline
\href{https://www.fftw.org/}{FFTW} & Fast Fourier Transform Library & Used to
translate signals from time to frequency domain efficiently. \\ \hline
\end{tabularx}
\caption{C/C++ libraries that will be used.}
\end{table}

\textbf{Python Libraries}
\begin{table}[h!]
\centering
\begin{tabularx}{\textwidth}{|l|X|X|}
\hline
\textbf{Library} & \textbf{Description} & \textbf{Usage} \\ \hline
\href{https://pypi.org/project/pyroomacoustics/}{pyroomaudio} & Room Acoustics
Simulation Library  & Used for prototyping audio array processing algorithms. \\
\hline
\href{https://numpy.org/}{Numpy} & Numerical Computing Library  & Used during
prototyping for handling larger computations. \\ \hline
\href{https://matplotlib.org/}{Matplotlib} & Plot Visualization Library  & Used
for plotting data. \\ \hline
\end{tabularx}
\caption{Python libraries that will be used.}
\end{table}

\subsection{Linter and Formatting Tools}

\href{https://clang.llvm.org/docs/ClangFormat.html}{ClangFormat} will be used
for autoformatting C/C++ code, ensuring compliance with the
\nameref{sec:coding_standards}. Additionally, Microsoft’s
\href{https://code.visualstudio.com/docs/languages/cpp}{C/C++ extension} in
Visual Studio Code will be used as the C/C++ linter.
\href{https://pypi.org/project/pylint/}{pylint} will be used as the Python
linter.

\subsection{Testing Frameworks}
\href{https://github.com/google/googletest}{GoogleTest} will be used as the main
testing framework for C/C++ code. Since Python will primarily be used for
prototyping and visualization, unit tests will generally not be written.
However, if correctness becomes critical,
\href{https://docs.pytest.org/}{pytest} will be used.

Code coverage for C/C++ will be measured using
\href{https://gcc.gnu.org/onlinedocs/gcc/Gcov.html}{gcov} and visualized with
\href{https://wiki.documentfoundation.org/Development/Lcov}{lcov}. Coverage
metrics will not be collected for Python tests if any are written.

\subsection{CI/CD}

\textbf{CI}
\begin{enumerate}
  \item Run all unit tests (\textit{PR blocking}).
  \item Build source code using a compiler compatible with the target
  microcontroller (\textit{PR blocking}).
\end{enumerate}
\textbf{CD} % Don't create a new line before here; else auto-indent.
\begin{enumerate}
    \item Generate and publish code coverage reports.
\end{enumerate}

\subsection{Performance Measuring Tools}
Due to hardware constraints of running on a microcontroller, performance
profiling will rely on the profiler available within the microcontroller’s IDE.

\subsection{Tools}
\begin{table}[h!]
\centering
\begin{tabularx}{\textwidth}{|l|X|}
\hline
\textbf{Tool} & \textbf{Description} \\ \hline
GitHub Projects (Kanban board) & Track issue progress and status. \\ \hline
GitHub Milestones & Organize and group GitHub issues. \\ \hline
\end{tabularx}
\caption{Tools that will be used.}
\end{table}

\subsection{Hardware Components}
\begin{itemize}
  \item Four microphones
  \item Analog to Digital Converter (ADC) modules, one per microphone
  \item Microcontroller
  \item Screen (monitor / smart glasses)
  \item Glasses frame
\end{itemize}


\section{Coding Standard}\label{sec:coding_standards}

\begin{table}[h!]
\centering
\begin{tabularx}{\textwidth}{|l|X|X|}
\hline
\textbf{Coding language} & \textbf{Coding Standard} \\ \hline
C & \href{https://www.gnu.org/prep/standards/html_node/Writing-C.html}{GNU C
coding standard} \\ \hline
C++ & \href{https://google.github.io/styleguide/cppguide.html}{Google C++} \\
\hline
Python & \href{https://peps.python.org/pep-0008/}{PEP8} \\ \hline
\end{tabularx}
\caption{Team adopted coding standards.}
\end{table}

\newpage{}

\section*{Appendix --- Reflection}

\input{../Reflection.tex}

\begin{enumerate}
    \item Why is it important to create a development plan prior to starting the
    project?

    \textbf{Omar Alam:} Creating a development plan for a large project is
    crucial to ensure that the team is aligned on goals and that expectations
    are understood by everyone. It helps keep everyone accountable since we are
    all agreeing to the same rules and any disagreements on processes can be
    resolved by referring back to the plan.

    \textbf{Kalp Shah}: Creating a development plan for projects of this scope
    is really important as it gives us guidelines to follow during development.
    With large projects such as these, we're bound to encounter many roadblocks
    but having a concrete development plan that all members of the team agree on
    (which is the most important part to me) gives us a good rulebook to look
    back on and follow. I find thinking about the technologies and workflows
    we'll use as not as important though, compared to the team communication and
    roles sections at least. I feel like the technologies and workflows tend to
    change as we learn more about the nature of the project, but having set
    defined roles and guidelines between the members that clarify how to deal
    with conflict, what expectations are, who should be responsible for what,
    etc. 
    
    \textbf{Nirmal Chaudhari:} Creating a development plan is important because
    it helps the team establish clear goals and standards. With everyone
    agreeing on the development plan, it will serve as a point of reference in
    the future, to ensure consistency among the team's work. It also helps the
    team begin thinking about the requirements of the project, and what research
    needs to be done going forward. 

    \textbf{Jay Sharma:} Creating a development plan is important because it
    provides a roadmap for the project. It helps the team stay on track and
    ensures that everyone is working towards the same goals. It also helps the
    team identify potential risks and challenges early on, so that they can be
    addressed before they become major problems.

    \textbf{Sathurshan Arulmohan:} A development plan serves as a guidance for
    the project. It lays out some of the key rules that the team agrees to
    adhere to, ensuring alignment and minimizing the risk of confusion or
    conflict later. Developing this plan also helps clarify priorities. For
    example, we have highlighted the importance of securing hardware components
    as early as possible and beginning software development on tasks that are
    independent of hardware availability.

    \item In your opinion, what are the advantages and disadvantages of using
    CI/CD?

    \textbf{Omar Alam}: CI/CD has many advantages, most of which tie back to the
    concept of iterative development. It allows us to ensure that the code
    branch that is considered production-ready ("main") is always in a
    deployable state. It also allows us to catch bugs when multiple developers
    are working on and merging in the same codebase. The main disadvantage of
    CI/CD is the intiial setup time and feasability of using it. In some cases,
    CI/CD may not be feasible which might end up applying to our project. This
    is mainly due to the embedded nature of our project and the lack of support
    for CI/CD on embedded systems. Furthermore, setting up unit tests in CI/CD
    will require us to write platform agnostic code that can also run on the
    embedded micro-controller and our development machines. This will require
    extra effort and guidelines to get right.

    \textbf{Kalp Shah}: CI/CD is really good, espeically for larger pojects with
    a team such as these. In my eyes, they help the most with maintainability -
    having a test suite and various workflows that execute after each small
    iteration of the project. This just helps us ensure that we're not going to
    break something that we didn't intend to break. Espectially as you continue
    to add many features on existing ones over the course of many months, where
    you've probably already forgotten what worked how they work or they were
    just implemented by another team member entirely. CI/CD really helps to act
    as the second pair of managing eyes to make sure that everyone's code is
    always compatible with the past and with each others, keeping a functional
    version of the project available at all times.The main disadvantage, though,
    is that it's a lot of setup, and has it's own amount of overhead for
    maintenance. For example, always ensuring that the test suite is up-to-date
    after each feature iteration. Although those are just good software
    practices, so maybe they are beneficial in that way too, who knows. But I'm
    sure that if we're not careful, we might end up with a lot of unnecessary
    workflows that just add to the complexity of the project.
    
    \textbf{Nirmal Chaudhari}: Using CI/CD enables our team to develop code in
    an agile context, thus allowing iterative improvement of key features in our
    project. Moreover, CI/CD also pushes us to validate our code more
    frequently, using automated pipelines. This ensures the quality of our code,
    and if configured correctly, can help ensure that our code meets the
    requirements we initially set. Despite these advantages, CI/CD may be
    limited when it comes to developing software or a product within a small
    time frame (like we are doing for our capstone). For projects with small
    deadlines, it may not be feasible to go with the iterative approach, since
    we may be forced to fully implement the project anyways. Also, when
    considering things outside of software, like embedded systems, iterative
    development doesn't really work if the hardware we are using is just a
    single component. 

    \textbf{Jay Sharma:} In my opinion, the main advantage of CI/CD is the
    reliability it brings to the development process - we can catch issues
    early, keep code deployable, and deliver features faster. The downside is
    that setting up and maintenance can be complex, and if not done well, they
    can slow things down instead of helping.
    
    \textbf{Sathurshan Arulmohan:} The main advantage of CI is automation of
    build checks and tests, ensuring that the software is always in a working
    state. This reduces the risk of introducing broken code into the main branch
    and provides developers with immediate feedback. In our project, this is
    especially useful since development occurs on different OS, and we may not
    have access to the same microcontroller compiler locally.

    The advantage of CD is that updates are automatically delivered to the
    target environment whenever new changes are merged. This ensures that the
    deployed system always contains the latest code, reducing manual effort.
    
    On the other hand, CI can sometimes hinder progress. For instance, if
    unrelated tests fail, developers may spend significant time debugging issues
    that are not caused by their own changes in a PR, slowing down feature
    delivery. Similarly, CD can introduce challenges when automatic deployment
    is not desirable. In some cases, it is preferable to release stable versions
    on a fixed schedule rather than pushing the latest changes immediately.

    \item What disagreements did your group have in this deliverable, if any,
    and how did you resolve them?

    \textbf{Omar Alam}: Since the team project is exepcted to require embedded
    hardware, we had disagreements on whether or not we could adequately specify
    elements needed to complete the "Expected Technology" section. We resolved
    this by researching the hardware we might end up using and determining that
    we could make reasonable assumptions on the technology we would be using.

    \textbf{Kalp Shah}: Personally, I don't think we had any disagreements on
    anything. I think there were just sections, however, that we were just
    unknowledgable about. For example, the "Expected Technology" section
    (hardware specifically) was one that sparked a lot of discussion since none
    of us had really worked with much hardware before - and definitely not in
    the field of audio processing. But after conducting some research and
    getting in touch with our supervisor (who gave us really good insight), we
    were able to move past that as well. 
    
    \textbf{Nirmal Chaudhari}: Our team didn't really have any disagreements
    while working on this deliverable. The only disagreement related to the work
    I was doing was naming convention for branches, and whether more than one
    issue should be implemented in a single branch. We resolved this by meeting
    up in person, and agreeing that a branch can contain multiple features. 
    
    \textbf{Jay Sharma:} In this deliverable, we experienced conflicting
    opinions on meeting times, branch names, and tools. However, we discussed
    options briefly, and voted on the best option. This kept us moving forward.

    \textbf{Sathurshan Arulmohan:} During this deliverable, our team faced
    challenges in defining roles and responsibilities. While everyone agreed
    that each member should have a clear role, there were disagreements about
    the significance and scope of certain roles, as some appeared to overlap
    with others. After discussion and careful consideration, we resolved this by
    introducing the System Specialist role, responsible for both hardware and
    software integration. Since our team is primarily software focused, having a
    dedicated member specializing in hardware provided balance and ensured
    smoother integration across the project.

\end{enumerate}

\newpage{}

\section*{Appendix --- Glossary}


\hypertarget{audio_classification_pipeline}{\underline{Audio Classification
Pipeline}}: Software pipeline aiming to classify the sound sources. For example,
the audio can be recognized as a car, person speaking, alarm, etc.

\newpage{}

\section*{Appendix --- Team Charter}

\subsection*{External Goals}

The team's primary goal is to gain expertise in embedded software development
while contributing a novel technique to the broader scientific and engieering
community. The main focus is that each member strengthens or acquires technical
skills that will be directly valuable in their future careers. As a stetch goal,
the team aims to rank within the top five projects at the Capstone Expo,
showcasing both technical innovation and professional presentation.

\subsection*{Attendance}

\subsubsection*{Expectations}

The team expects all members to attend all team meetings and to be punctual.
Every team member must indicate whether they will be attending by responding to
the Outlook meeting invites through their university emails. Team meetings will
begin at most 5 minutes after the scheduled start time. In-person meetings will
be preferred over virtual meetings. Virtual meetings will be held only when more
than 3 team members are unable to attend in person. If a team member is unable
to attend a meeting in-person, they may be able to attend virtually if it is
deemed viable by the rest of the team on a per meeting basis.

\subsubsection*{Acceptable Excuse}

Unfortunate circumstances may arise that prevent a team member from attending a
meeting. These circumstances include are encompassed in the following list:
\begin{itemize}
  \item Illness.
  \item Family emergency.
  \item Medical or academic related appointment.
  \item Religious holiday.
  \item Other circumstances agreed upon by all team members.
\end{itemize}

\subsubsection*{In Case of Emergency}

Try to predict absences beforehand, but emergencies still arise despite best
efforts. In the case of an emergency, the absent team member must notify the
team as soon as possible through Microsoft Teams. If the emergency is expected
to last for a prolonged period of time, please refer to instructions provided by
the course instructor to communicate with the Associate Dean.

\subsection*{Accountability and Teamwork}

\subsubsection*{Quality} 

Our team expects all members to come to meetings fully prepared with completed
work, clear progress updates, and constructive contributions to discussions. All
deliverables must meet our established quality standards including proper code
review, testing, and thorough documentation. We emphasize proactive
communication, early problem identification, and mutual support to ensure the
team's success and maintain high professional standards throughout the project.

\subsubsection*{Attitude}

We expect all team members to maintain a positive, collaborative attitude and
treat each other with respect and professionalism. We encourage open
communication, constructive feedback, and diverse perspectives while ensuring
all interactions remain productive and inclusive. Our team adopts a conflict
resolution approach that prioritizes direct communication, active listening, and
finding mutually beneficial solutions to maintain a supportive working
environment.

\subsubsection*{Stay on Track}

We will track team performance through regular check-ins, commit frequency, and
meeting attendance to ensure everyone contributes their fair share. For members
who exceed expectations and consistently deliver quality work, we will reward
them with treats like Tim Hortons coffee or donuts to recognize their efforts.
For those not contributing their fair share, we will initially cover for them
and provide support, but after repeated instances, we will issue formal warnings
and escalate to our TA or instructor if necessary to maintain team
accountability and project success.

\subsubsection*{Team Building}

We will build team cohesion by hosting social gatherings at our off-campus
house, where we can work together on projects in a relaxed environment and spend
time hanging out to strengthen our relationships. These informal settings will
help us bond as a team while still maintaining productivity and collaboration on
our project goals.

\subsubsection*{Decision Making} 

We will make decisions through consensus when possible, seeking common ground
and agreement among all team members. However, when there is a clear divide or
disagreement that cannot be resolved through discussion, we will hold a formal
vote to reach a decision and move forward with the project. This approach
ensures we respect everyone's input while maintaining progress when consensus
cannot be achieved.

\end{document}