\documentclass[12pt, titlepage]{article}

\usepackage{amsmath, mathtools}

\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{colortbl}
\usepackage{xr}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{xfrac}
\usepackage{tabularx}
\usepackage{float}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[section]{placeins}
\usepackage{caption}
\usepackage{fullpage}
\usepackage{cite}
\usepackage{breqn}

\input{../../Comments}
\input{../../Common}

\externaldocument[SRS-]{../../SRS/SRS}

\begin{document}

\title{Hardware Report\\\progname}

\author{\authname}

\date{}

\maketitle

\pagenumbering{roman}

\newpage
\section{Revision History}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Dec 21, 2025 & Sathurshan, Omar & Report outline.\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\tableofcontents

\newpage

\pagenumbering{arabic}

\section{Introduction}
\wss{Explain the prupose of this document. Why it was selected for this project}
\wss{Briefly outline the structure of the document}

\section{Hardware}

\subsection{Hardware Requirements}
\wss{Write down requirements that applied to hardware from SRS.}
\wss{Write down any constraints (budget)}

\subsection{Required Hardware Conponents}
\wss{List what hardware is required based on the requirements from above section.}
\wss{Explain how each hardware acheives each requirements/ why it is needed?}
\wss{microcontroller, microphone, Rokid glasses \cite{RokidGlasses}}

\subsection{Hardware Selection Process}
\wss{Process of selecting hardware to fit requirements and pricing}
\wss{performance, cost, timing of shipment, etc.}
\wss{Aleternative hardware}
\wss{Include links to hardware source}

\subsection{Hardware Specification}
\wss{Include specification table of each hardware.}
\wss{Include links to manufacturing documentation whether online or in this repo}

\subsubsection{STM microcontoller}

\subsubsection{Microphone}
\wss{Go over each pin}

\subsubsection{Rokid AR glasses}

\section{Theory}
\wss{This section goes over some theory, that will help understand the
hardware integration section}

\subsection{I2S Communication Protocol}
\wss{Explain what is I2S? How it represents data?}

\subsection{Micophone Synchronization}
\wss{Explain what mic Synchronization is. Why is it important?}
\wss{How can multiple microphones be Synchronized on the same clock}

\section{Hardware Integration}

\subsection{Wiring}
\wss{Provide images and explanation of wiring}

\section{Software-Hardware Integration}

\wss{Explain this section is to provide more context how software was designed
for the hardware. Main point to point out how software engineering is relevant
since this is a software capstone.}
\wss{System diagram with hardware layer at the bottom}
\subsection{Software Architecture}
\wss{briefly go over software architecture}
\wss{libraries used related to hardware}

\subsection{Hardware Abstraction Layer}
\wss{Describe the hardware abstraction strategy. (benefits or portability and maintainability)}

\subsection{Hardware Interface Implementation}
\wss{Overview of manufacturer code}
\wss{Point to the hardware layer code.}
\wss{What interfacing code had to be implemented and why?}

\newpage 

\bibliographystyle{IEEEtran}
\bibliography{../../../refs/References}

\end{document}