\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}
\usepackage{cite}
\usepackage{xr}

\externaldocument[DevPlan-]{../DevelopmentPlan/DevelopmentPlan}


\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\newpage

\tableofcontents

\newpage

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation; the contributions prior to Rev0 are
NOT included.

\section{Team Meeting Attendance}

Team meetings are held weekly to ensure that the team is on track with the
project towards the final deliverable. Meetings were used to discuss about
updates, blockers and next steps.

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 6\\
Omar Alam & 6 \\
Sathurshan Arulmohan & 6 \\
Nirmal Chaudhari & 6 \\
Kalp Shah & 5 \\
Jay Sharma & 6 \\
\bottomrule
\end{tabular}
\end{table}

\section{Supervisor/Stakeholder Meeting Attendance}

The team did not meet with the supervisor during this period, as the goal for
revision 0 had been successfully achieved and met expectations by the
supervisor. Dr. Martin V. Mohrenschildt was selected as the team's supervisor
due to his expertise in signal processing. With all signal processing features
completed in revision 0, efforts during this time were directed toward testing
and refining the existing algorithms which did not require supervisor meetings.

The team was not able to meet with the project's primary stakeholder, McMaster
Sign Language club. The team has attempted to reach this club via email,
however, did not receive any response.

\noindent \textbf{Supervisor's Name: }Dr. Martin V. Mohrenschildt

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 0\\
Omar Alam & 0 \\
Sathurshan Arulmohan & 0 \\
Nirmal Chaudhari & 0 \\
Kalp Shah & 0 \\
Jay Sharma & 0 \\
\bottomrule
\end{tabular}
\end{table}

\section{Lecture Attendance}

The team agreed that at least one member would attend each lecture and take
notes, with Nirmal designated as the
\hyperref[DevPlan-role:note_taker]{Note Taker}. In cases where Nirmal
was unable to attend, another team member served as a substitute. The team
successfully ensured that at least one representative attended every lecture.

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Omar Alam & 1 \\
Sathurshan Arulmohan & 0 \\
Nirmal Chaudhari & 0 \\
Kalp Shah & 0 \\
Jay Sharma & 0 \\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\noindent \textbf{TA's Name: }Rashad Bhuiyan

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Omar Alam & 1 \\
Sathurshan Arulmohan & 0 \\
Nirmal Chaudhari & 1 \\
Kalp Shah & 1 \\
Jay Sharma & 1 \\
\bottomrule
\end{tabular}
\end{table}


\section{Commits}

Commit data metrics date ranges from February 5, 2026 to March 25, 2026.
The following command was used to extract this metric:\\
\textit{git shortlog -sne --since="5 Feb 2026" --before="25 Mar 2026"}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 228 & 100\% \\
Omar Alam & 32 & 14.0\% \\
Sathurshan Arulmohan & 78 & 34.1\% \\
Nirmal Chaudhari & 52 & 22.8\% \\
Kalp Shah & 53 & 23.4\% \\
Jay Sharma & 13 & 5.7\% \\
\bottomrule
\end{tabular}
\end{table}

There are work that is not counted in commit count such as the User Testing
completed by Jay, and the hardware improvements completed primarily by Omar.

\section{Issue Tracker}

Sathurshan has a higher number of authored issues, as it is the
\hyperref[DevPlan-role:leader]{Leader's} responsibility to create and assign
tasks to team members for each milestone. This role distribution was agreed
upon by the team, as outlined in the Development Plan document
\cite{DevelopmentPlan}.

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Omar Alam & 0 & 21 \\
Sathurshan Arulmohan & 63 & 35 \\
Nirmal Chaudhari & 0 & 24 \\
Kalp Shah & 1 & 22 \\
Jay Sharma & 0 & 21 \\
\bottomrule
\end{tabular}
\end{table}

\section{Team Charter Trigger Items}

There have been no team charter trigger items to date. The team has the project
in a state that is ready to present and teammates have made many instances of 
improvements to the project in terms of usability, testing, performance, and
accuracy of algorithms.

\newpage
\bibliographystyle{IEEEtran}
\bibliography{../../refs/References}

\end{document}